\section{Design and Implementation}
\label{sec:design}

\subsection{Receive-Path Execution Model}
\label{sec:design-model}

WireGuard separates decryption order from delivery order.  On receive, a data
packet is first appended to a per-peer \emph{ordered queue} and marked
\textsc{uncrypted}.  The same packet is then published to a
device-wide decrypt ring.  The ring feeds per-CPU workers from WireGuard's
cryptographic workqueue; it may contain packets from any peer attached to that
WireGuard device.  A worker consumes a ring entry, authenticates and decrypts
it, and changes its state to \textsc{crypted}, or to \textsc{dead} on
failure~\cite{wireguard-linux,linux-workqueue}.

These two queues deliberately enforce different constraints.  The device ring
allows workers to decrypt independent packets in parallel.  The per-peer queue
records arrival order and has one consumer: that peer's NAPI receive
poll~\cite{linux-napi}.  The poll examines the ordered head and removes entries
only after an acquire load observes a terminal state.  A \textsc{crypted}
packet proceeds through replay validation and normal stack delivery; a
\textsc{dead} packet is drained and freed.  An \textsc{uncrypted} head stops
the loop.  Consequently, a later packet may have completed decryption but
cannot pass an earlier incomplete head.

This is the execution-order inversion addressed here.  Decryption completes in
worker execution order, while the receive poll must commit packets in arrival
order.  When those orders differ, the NAPI consumer can be runnable yet unable
to deliver.  Pending decrypt jobs can simultaneously remain in the shared
device ring.

\subsection{Detecting an Ordered-Head Stall}
\label{sec:design-detection}

The implementation detects blocking at the point where the existing ordered
delivery loop stops.  After peeking the per-peer queue, it reads the head state
with acquire semantics.  A present head whose state remains
\textsc{uncrypted} is an ordered-head stall; an empty queue is a distinct
condition.  This distinction matters because neither a wake nor work stealing
can make progress for the same reason in both cases.

For mechanism validation, optional instrumentation records contiguous blocked
episodes under the class observed when the episode opens.  Separate arrays
store the episode count, cumulative and maximum duration, and four duration
buckets for empty-queue and \textsc{uncrypted}-head episodes.  Additional
counters classify the head state against the NAPI \textsc{missed} bit and
record work-stealing pulls, unblocking passes, and zero-pull dry runs.  These
global counters are intentionally lightweight, racy integer accumulators.
They support descriptive ratios and order-of-magnitude comparisons, not exact
concurrent accounting or inferential endpoints.

\subsection{Wake-Side Mechanisms}
\label{sec:design-wake}

Before changing where decryption executes, we implemented two complementary
wake-side mechanisms (Table~\ref{tab:design-knobs}).  They address polls that
are scheduled before the ordered head can be delivered, but they do not
perform pending decrypt work.

\paragraph{Consumer-side suppression (\texttt{wg\_supp}).}
When a poll is about to complete with an \textsc{uncrypted} head, a concurrently
completed non-head packet may have set NAPI's \textsc{missed} bit.  Leaving the
bit set immediately reschedules the poll, which observes the same incomplete
head and does no useful work.  The suppression path clears \textsc{missed},
executes an ordering barrier, and rechecks the head.  If the head became
terminal during that window, it restores \textsc{missed}; otherwise the poll
parks until a later completion schedules it.  This recheck prevents a
completion racing the clear from being lost.

\paragraph{Producer-side head gating (\texttt{wg\_headwake}).}
At the completion point, a worker ordinarily requests NAPI execution for every
packet.  Head gating instead lets the poll publish the packet on which it is
blocked.  A producer schedules NAPI only when it completes that exact packet,
or when the poll observed an empty queue and any new packet becomes the head.
The producer compares the published pointer but never dereferences it.
Store-release publication of the packet state, a full barrier, and the poll's
publish-then-recheck sequence form a two-sided lost-wakeup protocol.  Error
completions remain on the immediate wake path so that \textsc{dead} entries are
drained.

\input{tables/design_knobs}

The two mechanisms compose: head gating suppresses producer wakes for
non-head completions, while consumer suppression clears a \textsc{missed}
reschedule that reached the poll through a concurrent path.  Both reduce
premature execution.  Neither changes the \textsc{uncrypted} head's state, so
neither can directly shorten an episode in which pending decryption is the
missing prerequisite.

\subsection{Bounded Receive-Side Work Stealing}
\label{sec:design-steal}

\texttt{wg\_steal} acts after the normal delivery loop reaches an
\textsc{uncrypted} head and before the poll completes.  If the treatment is
enabled and delivery budget remains, the current NAPI/softirq CPU consumes an
entry from the device-wide decrypt ring using the same locked consume primitive
as a normal worker.  It decrypts the returned packet synchronously and invokes
WireGuard's normal per-peer receive-completion function with the resulting
\textsc{crypted} or \textsc{dead} state.  The completion may concern any peer:
the ring is device-wide, and the stolen entry need not be the head that caused
the current poll to block.

After each completion, the steal loop rechecks the current peer's ordered
head.  It stops when the head is absent or terminal, the configured number of
jobs has been consumed, or the device ring is empty.  Ring emptiness does not
mean no decryption is in progress: a normal worker may already have removed
the relevant head and be processing it.  Workers continue to run concurrently
with the stealing poll.

If at least one job was pulled and the current head has become terminal, the
poll returns to the original delivery loop.  No stolen packet is injected
directly into the network stack.  A job first completes through the normal
per-peer path, and delivery still removes packets from the ordered queue.
Thus work stealing changes which context executes decryption, not the order in
which packets become visible above WireGuard.

\subsection{Ownership and Ordering Preservation}
\label{sec:design-safety}

Exclusive ownership follows from the existing ring interface.  Both per-CPU
workers and the NAPI stealing path call the bottom-half-safe consume operation,
which holds the ring's consumer lock while removing one entry.  A successful
consume advances the ring and transfers the returned packet to exactly one
caller.  A worker and the NAPI path therefore cannot consume the same ring
element.

State publication follows the stock synchronization discipline.  Enqueue first
marks a packet \textsc{uncrypted} with release semantics, records it in the
per-peer queue, and then publishes it to the device ring.  The unique consumer
performs decryption and calls the normal completion helper, which publishes
\textsc{crypted} or \textsc{dead} with a release store.  The NAPI consumer reads
that state with acquire semantics.  Peer and key references, replay checks,
error draining, and stack delivery are unchanged.  In particular,
\texttt{wg\_steal} never removes an entry from the per-peer ordered queue and
cannot bypass the head.

These properties provide a source-level safety argument for exclusive ring
ownership and order preservation.  They are not a formal proof of all lifetime,
scheduling, or cross-version properties.  The evaluation additionally checks
for kernel warnings, stalled handshakes, and failures in the tested campaigns,
but absence of an observed failure is not evidence of production safety.

\subsection{Selecting and Bounding the Steal Budget}
\label{sec:design-budget}

The parameter is a per-\emph{pass} bound.  With
\texttt{wg\_steal=4}, one entry into the steal loop can successfully consume at
most four jobs.  It may consume fewer because the ring becomes empty or the
ordered head becomes terminal.  Four denotes neither decryption workers nor
CPUs, and it is not guaranteed that four jobs are available.

Nor is four necessarily a limit for an entire NAPI poll.  When a pass unblocks
the head, the same poll returns to delivery.  It can later reach another
\textsc{uncrypted} head and enter a new steal pass whose local counter starts
at zero.  A complete poll can therefore steal more than four jobs in total.
The ordinary NAPI budget still bounds delivered packets, but synchronous
decrypt time is not charged to the poll's \texttt{work\_done} count.

This accounting motivates a small bound.  A large value could extend
bottom-half execution, delay other softirq work, or consume jobs belonging to
other peers.  The bound limits each uninterrupted pull sequence, while the
evaluation separates exploratory budget selection from the final paired test
of budget four.

\subsection{Implementation Limitations}
\label{sec:design-limitations}

The prototype trades scheduling delay for synchronous work in softirq context.
That trade can be favorable when one RX/softirq core is the binding resource,
but it creates three limitations.  First, a device-wide steal is not
peer-local, so the blocked peer may perform work that benefits another peer.
Second, stolen crypto is not represented in NAPI's delivery accounting, which
weakens the budget's relationship to CPU time.  Third, longer bottom-half
execution can affect fairness and scheduler latency even when throughput or
aggregate CPU improves.

The implementation is therefore a research prototype.  The experiments test
specific Linux 5.15, CloudLab c220g2, traffic, and budget configurations.  A
production design would require broader kernel validation, an explicit
time-based or work-accounting policy, multi-peer fairness measurements, and a
loss-tolerant latency study.
