\section{Related Work}
\label{sec:related}

Our mechanism sits at the intersection of kernel VPN performance, receive-side
scaling, ordered parallel processing, and work stealing. We position it against
each, and state plainly what it is not: not a new tunnel protocol or cipher, not
a receive-steering algorithm, and not a general-purpose task scheduler. It is a
bounded receive-path mechanism that operates inside WireGuard's existing
ordering model.

\paragraph{WireGuard and its receive path.}
WireGuard~\cite{donenfeld2017} is an in-kernel VPN built on the Noise
framework~\cite{noise} and ChaCha20-Poly1305~\cite{rfc8439}. Its receive path
decrypts in parallel and delivers in order, which is the source of the inversion
we study.
% TECHNICAL REVIEW: confirm this one-line characterization of prior work is
% accurate -- that mounah2025 improves the same WireGuard receive path by
% changing where deferred receive processing executes. This claim is not
% covered by CLAIM_EVIDENCE_MATRIX.md; the same summary appears once in
% 02-introduction.tex (paragraph 4).
Closest to our work, \citet{mounah2025} analyze kernel asynchronous
APIs in a kernel VPN and improve the same receive path by changing where
deferred receive processing executes, lowering the cost that a related inversion
imposes. We take a different lever: instead of relocating or cheapening the
deferred work, we let the blocked delivery context advance the pending
decryption that it is waiting on. Kernel-bypass designs such as
XDP~\cite{hoiland2018xdp} avoid the stack entirely to reach high rates;
WireGuard deliberately stays in the kernel networking stack, and our mechanism
does too, so it inherits the same interoperability and isolation.

\paragraph{NAPI and receive steering.}
Interrupt mitigation through NAPI is long-standing~\cite{salim2001beyond}, and
receive-side scaling distributes flows across cores by hashing flow identifiers,
with software variants and connection-placement schemes improving
locality~\cite{linux-napi,pesterev2012affinity}. These techniques operate
\emph{between} flows: they choose which core serves a flow. They cannot divide a
single WireGuard tunnel, whose fixed outer five-tuple hashes to one queue. Our
mechanism is orthogonal and complementary: it acts \emph{within} the one RX/NAPI
context that a single tunnel is bound to, exactly the case steering cannot
spread.

\paragraph{Parallel processing with ordered completion.}
Reconciling parallel execution with ordered output is a recurring kernel
problem. The \texttt{padata} framework parallelizes IPsec cryptography across
cores and restores order through a dedicated serialization
stage~\cite{linux-padata}. WireGuard instead records arrival order in a per-peer
queue and decrypts through a device-wide ring, so ordering is enforced at the
single delivery consumer rather than by a reorder stage. We do not add a
reordering stage, and our implementation is not \texttt{padata}; we keep the
existing per-peer ordered queue and let the blocked consumer make progress on
the shared decrypt work. Head-of-line blocking of this kind is general to
ordered parallel pipelines, but here it is specific to the boundary between
parallel decryption and single-consumer ordered delivery, which is what our
design targets.

\paragraph{Work stealing and cooperative execution.}
Work stealing is a classic load-balancing discipline: an idle worker takes tasks
from a busy worker's deque, with strong bounds and a widely used runtime
realization in Cilk~\cite{blumofe1999,frigo1998cilk}. Our mechanism borrows the
name but differs in intent and structure. The context that steals is not an idle
worker seeking load balance; it is a delivery consumer blocked on an ordering
constraint. It pulls from a single shared ring rather than from per-worker
deques, its budget is small and bounded per pass, and its goal is to unblock
ordered delivery rather than to maximize parallel throughput. In that respect it
is closer to cooperative schemes such as flat combining, where one thread
performs others' pending operations to reduce
synchronization~\cite{hendler2010flat}: \texttt{wg\_steal} likewise has the
blocked context perform pending work, but to relieve a single-core receive
bottleneck, within a hard bound, and in softirq context. These constraints, and
the ordering guarantee they preserve, are what distinguish a receive-path
scheduling mechanism from a general-purpose work-stealing scheduler.
