\section{Conclusion}
\label{sec:conclusion}

WireGuard's parallel decryption and ordered delivery create an execution-order
inversion: a later packet can finish before the ordered head, and the receive
poll then stalls with useful decrypt work still pending. We showed that
suppressing the premature polls this inversion produces is real but reclaims
little CPU on the tested hardware, because the entire empty-poll population
occupies only about two hundredths of a core. The more consequential cost is the
tens of microseconds delivery spends blocked behind an incomplete head, where
the head waits to be scheduled onto a worker rather than to be decrypted.
\texttt{wg\_steal} targets that interval: the blocked NAPI context performs a
bounded amount of pending decrypt work from the device-wide ring before
yielding, entirely within WireGuard's existing ordering.

In the uncapped saturated single-tunnel regime, where one receive core is the
binding resource, stealing raised throughput and reduced total CPU, its two
co-primary endpoints. At an exactly matched load near 3.8~Gb/s, no favorable CPU
effect was detected, even though mechanism counters show the classified
blocked-head population was still nearly eliminated. This cross-regime pattern is
consistent with the benefit becoming measurable as the pinned receive core
approaches its binding limit. The two campaigns do not establish a saturation
threshold or a formal treatment-by-saturation interaction, and we make no
user-visible latency claim.

The mechanism is a research prototype, and its limits point to concrete next
steps. Stolen decryption runs in softirq and is not charged to NAPI's delivery
budget, so a production design should account that work against a scheduling
budget to bound softirq duration and to measure per-peer fairness, especially
because a stolen job may belong to another peer. The effect should be validated
across NICs, CPUs, and kernel versions, and the withdrawn closed-loop latency
probe should be replaced by a loss-tolerant, open-loop study. More broadly, the
result frames a question for any ordered parallel receive path: when a delivery
consumer is blocked on work owned by another scheduling path, letting it advance
that work under a strict bound is a lever worth measuring wherever one core is
the receive-side ceiling.
